\Large Analyzing the Supreme Court Citation Network

### 2017-12-24 Tex/paper.tex
added in Ted's section

\textbf{TED}, would you write a section that covers the ways in which network scholars have studied citations in the past, focusing on scientific papers, patents, and court cases?

>>>>

A citation is a directed link between two documents that indicates the citing document attributes the cited to be in some manner relevant to it. Collective patterns of citations within a certain domain make up citation networks, which are most commonly found in three social systems, scientific publishing, patents, and the judicial system. When raw citation data is formally represented as a network, the nodes are usually the documents themselves, and each directed arc, usually unweighted, is the existence of one or more cites from the sending to the receiving document. Given the permanent nature of documents in citations networks, these networks are in large acyclic \citep{leicht2007large,karrer2009random}. Relatedly, citation networks grow as new documents and citations enter the network, but established arcs persist in all but exceptional cases.

	In its raw form a citation is a link between two documents, but it is the result of human judgment about the utility of the cite \citep{fowler2008authority}. Studies of citation networks can be broadly categorized according to whether they treat this set of observed behavioural patterns as information that can be used to understand different aspects of the system, or treat them as outcomes to be modeled. We discuss these in turn.

	First, as these arcs are observed patterns of behaviour, they can be used to infer latent characteristics of nodes or the relations between nodes that produced them \citep{batagelj2003efficient}. Moreover, since each judgment is embedded in the broader network of citations, which influences the judgment beyond the characteristics of the two directly linked documents, inferences about the neighborhood of these two documents are possible as well. A common application of this general logic is to obtain local or global network indices, such as Kleinberg centrality at the node level \citep{kleinberg1999authoritative,fowler2007network} or global hierarchy \citep{mones2014universal}, then use them to draw conclusions about networks or compare networks across contexts such as time periods \citep[e.g.][]{vazquez2001statistics,fowler2008authority,greenberg2009citation,lupu2012precedent,lupu2013strategic,dawson2014current,jaffe2017patent}.

	Still within the category of using observed network constellation to make inferences about components of the system, identification of communities using methods for clustering, such as modularity maximization \citep[e.g.][]{kajikawa2007creating,shibata2011detecting,chen2010community} and stochastic block modeling \citep{jo2009citing}; and subnetwork identification \citep[e.g.][]{batagelj2017emergence} have been used to analyze relevance of topics within an academic field or to determine trends in technological advancement \citep{verspagen2007mapping,erdi2013prediction}. Main path analysis \citep{hummon1989connectivity}, which determines the main path through an acyclic network, is a particularly useful way to examine trends as it allows researchers identify structures of knowledge flow. Other methods include classifying documents into groups based on similarities in their citation profiles of cites over time, which can be examined as a function of time to see if there are temporal patterns \citep{leicht2007large}. The identification of communities is often coupled with classification of these communities by the researcher using historical knowledge.

	Researchers are also interested in understanding the mechanisms that drive citations between documents. Work in this area generally proceed by specifying a set of citation behaviour, then proposing a model to capture the combination of these behavioural rules \citep{simkin2007mathematical}. Assessment of the model is based on how well it fit citation distributions. Researchers working in this area tend to focus on modeling the growth of the citation network as governed by a degree-based mechanism such as preferential attachment \citep{barabasi1999emergence} or the recursive search \citep{vazquez2001statistics}, and the age of the paper \citep{jeong2003measuring,eom2011characterizing,wang2013quantifying}. Regarding age, the previous standard approach was to treat the probability of citation as a separable function of degree and age \citep{hajra2005aging,hajra2006modelling}, then examine the distribution of citations, scaled to the rate of new publications, by age. More recently, work has been done in relaxing the assumption that the effect of degree is static, instead allowing it to vary with time \citep{wang2008measuring}.

	Another approach to understanding the generative process of citation networks is to examine the existence of network motifs, or subnetwork structures, that can be interpreted as measuring different generative mechanisms. One way of doing so is to compare the observed network statistics to a null distribution. This null model must also be characterized by features of citation networks discussed earlier, meaning that it must be a directed acyclic graph with unweighted arcs \citep{carstens2016topology}. Two sets of uniform random graph models have been proposed for directed acyclic graphs. In the former, \citet{karrer2009random} introduce two uniform random graph models based respectively on fixed-degree sequence and fixed-expected degree sequence. Both models preserve the requisite characteristics of citation networks with the exception that they can introduce weighted edges with low probability, which leads to networks from the null distribution to be sampled with nonequal probability. \citet{carstens2014uniform,carstens2016topology} introduces a model that preserves the requisite characteristics and also do not introduce weighted arcs. Loosely related is an egocentric framework, introduced by \citet{vu2011dynamic}, that models continuous-time network data through a multivariate counting process, which can be used to count network motifs.

	\section{Extra Notes}
	This section contains some of the extra notes I cut out from the draft that might be useful.
	\subsection{Broader definitions of citation networks}
	More broadly, citation networks can have as nodes the document producers, including scientists \citep{ji2016coauthorship}, judges \citep{landes1998judicial}, journals \citep{rice1988citation}, or aggregated units \citep{gelter2012networks,pan2012world}. In these cases, which are essentially exercises in aggregation, the resulting network can take on different characteristics such as weighted or cyclic edges. Other networks derived from the raw citation network is the co-citation or co-cited-by networks whereby two documents are connected if they co-cite or are co-cited by another document \citep{van2005reference}.

	\subsection{Weighted edges and multiplexity}
	Recognition, and subsequent quantification, of different levels of complexity in citation arcs allows for a host of advancements in citation network analysis. Weights can indicate relevance \citep{liu2014citations} or be used to incorporate the temporal dimension into citation networks \citep{fujita2014detecting}. Moving to multiplexity leads to further advancements. For example, \citet{greenberg2009citation} accounted for level of support and through simulations based on arc typed switching demonstrated how citation bias against critical articles yielded differences in beliefs within a medical discipline. \citet{bommarito2010distance} argued that articles contain different types of information and accounting for the specific piece of information that resulted in the cite can yield clustering that are more interpretable. In all cases however, substantial work has to be done into reclassifying the weightedness or multiplexity of citation arcs \citep{zhang2007semantics}.

	\subsection{Misc. notes}
	\begin{itemize}
		\item To control for age, \citet{clough2015transitive} propose transitive reduction of citation networks (i.e. removal of redundant information ties) as it will primarily remove citation arcs that are disparate in age.
		\item Most citation networks are directed acyclic graphs, but not all. Different versions of the same document can also cause problems (such as strong network components). The ``preprint transformation'' is a solution to small strong components \citep{batagelj2017emergence}.
		\item Date of publication can be assigned as level to nodes in acyclic networks \citep{batagelj2017emergence}. Depending on the citation network at hand, temporal ordering can be difficult, as documents can share publication dates. To overcome this, begin each iteration by sampling from one of the possible orderings. \citep{carstens2016topology}.
	\end{itemize}
